Recursive Neural Network Part-of-Speech Tagger

### 2013-12-21 paper/paper.tex
Add argmax.

@@

For instance, given the sentence $(w_{i_1},w_{i_2},\ldots,w_{i_K})$ of length $K$, we first calculate the word representations $V\Ket{w_{i_1}},\ldots,V\Ket{w_{i_K}}$, then we calculate each phrase representation $p_j$ from the previous phrase representation $p_{j-1}$ and the current word representation $V\Ket{w_{i_j}}$ by concatenating the two representation vectors, multiplying by $W_{combine}$ and adding $b_{combine}$ before applying the $tanh(\cdot)$ function:
$$p_j = tanh(W_{combine}\Big[p_{j-1};V\Ket{w_{i_j}}\Big] + b_{combine})$$
Subsequently, each $p_j$ is passed along to the classifier, which applies the operation:
$$t_{i_j} = softmax(W_{classify}p_j + b_{classify})$$
to obtain the predicted tag $t_{i_j}$ for $w_{i_j}$.

>>>>

\newcommand{\argmax}{\operatornamewithlimits{argmax}}

@@

For instance, given the sentence $(w_{i_1},w_{i_2},\ldots,w_{i_K})$ of length $K$, we first calculate the word representations $V\Ket{w_{i_1}},\ldots,V\Ket{w_{i_K}}$, then we calculate each phrase representation $p_j$ from the previous phrase representation $p_{j-1}$ and the current word representation $V\Ket{w_{i_j}}$ by concatenating the two representation vectors, multiplying by $W_{combine}$ and adding $b_{combine}$ before applying the $tanh(\cdot)$ function:
$$p_j = tanh(W_{combine}\Big[p_{j-1};V\Ket{w_{i_j}}\Big] + b_{combine})$$
Subsequently, each $p_j$ is passed along to the classifier, which applies the operation:
$$t_{i_j} = \argmax\limits_{t} softmax(W_{classify}p_j + b_{classify})$$
to obtain the predicted tag $t_{i_j}$ for $w_{i_j}$.
